Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-17 vesicle_code/docs/adhesion/adhesion.tex
adding new images

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep01.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep02.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep03.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep04.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep05.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep06.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep07.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep08.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep09.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep10.pdf}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the adhesion strength is $0.7$, the
adhesion length scale is $0.4$, and the shear rate is $\chi=1$.}
\end{figure}

\begin{figure}
  \todo[inline]{Fix and finish right figure}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{{\em Left}: Distance between a pair of vesicles in a planar
    shear flow with shear rate $\chi=1$ and adhesion length scale
    $\delta = 0.4$.   The different lines correspond to a linear spacing
    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
    critical vdW potential strength $\sigma$ for binding of two vesicles
    in a shear flow depends on the shear rate $\chi$.
  \label{fig:sflow_phase_diagram}}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the Hamaker contsant is $\sigma=0.7$, the
adhesion length scale is $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

\begin{figure}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{{\em Left}: Distance between a pair of vesicles in a planar
    shear flow with shear rate $\chi=1$ and adhesion length scale
    $\delta = 0.4$.   The different lines correspond to a linear spacing
    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
    critical vdW potential strength $\sigma$ for binding of two vesicles
    in a shear flow depends on the shear rate $\chi$.
  \label{fig:sflow_phase_diagram}}
\end{figure}
